Step 14: Export All Results

### 2025-09-08 reanalysis-12-marginal_effects.qmd
reorganize

    # Display table - simplified to avoid kable errors
    print(kable(summary_df,
          caption = "Pooled Average Marginal Effects of Lapsing by Subgroup",
          align = c("l", "r", "r", "c", "r", "r", "r"),
          digits = 4))

    # Save to CSV
    write.csv(summary_df, 
              file.path(marginal_effects_dir, "marginal_effects_summary.csv"),
              row.names = FALSE)
    log_message("Saved summary table to CSV")
  } else {
    cat("No successful results to display in summary table\n")
    log_message("No successful pooled results for summary table")
  }
} else {
  cat("No pooled results available for summary table\n")
  log_message("No pooled results found")
}
```

@@

# Define order for plots (reversed for coord_flip)
subgroup_order <- rev(c(
  "No DR or NPDR, no treatment", "No DR or NPDR, any treatment", 
  "NPDR, no treatment", "NPDR, any treatment", 
  "Mild NPDR, no treatment", "Mild NPDR, any treatment",
  "Moderate NPDR, no treatment", "Moderate NPDR, any treatment",
  "Severe NPDR, no treatment", "Severe NPDR, any treatment",
  "PDR, any treatment", "PDR, on anti-VEGF only", "PDR, on PRP only"
))

@@

log_message("Results exported")
cat("\n✓ Results exported to:", marginal_effects_dir, "\n")
```

>>>>

    # Display table properly in Quarto (no print needed)
    kable(summary_df,
          caption = "Pooled Average Marginal Effects of Lapsing by Subgroup",
          align = c("l", "r", "r", "c", "r", "r", "r"),
          digits = 4)

    # Save formatted summary to CSV
    write.csv(summary_df, 
              file.path(marginal_effects_dir, "marginal_effects_summary.csv"),
              row.names = FALSE)

    # Also save a numeric version for easier analysis
    numeric_df <- do.call(rbind, lapply(names(pooled_mfx), function(sg_name) {
      res <- pooled_mfx[[sg_name]]
      if (!is.null(res) && !is.null(res$success) && res$success) {
        data.frame(
          subgroup = sg_name,
          subgroup_label = res$name,
          ame = res$ame,
          se = res$se,
          ci_lower = res$ci_lower,
          ci_upper = res$ci_upper,
          z_stat = res$z_stat,
          p_value = res$p_value,
          avg_n = res$avg_n,
          n_imputations = res$n_imputations,
          df = res$df,
          stringsAsFactors = FALSE
        )
      }
    }))

    write.csv(numeric_df,
              file.path(marginal_effects_dir, "marginal_effects_numeric.csv"),
              row.names = FALSE)

    log_message("Saved summary tables to CSV (formatted and numeric)")
  } else {
    cat("No successful results to display in summary table\n")
    log_message("No successful pooled results for summary table")
  }
} else {
  cat("No pooled results available for summary table\n")
  log_message("No pooled results found")
}
```

@@

# Define order for plots (reversed for coord_flip)
subgroup_order <- rev(c(
  "No DR or NPDR, no treatment", "No DR or NPDR, any treatment", 
  "NPDR, no treatment", "NPDR, any treatment", 
  "PDR, any treatment", "PDR, on anti-VEGF only", "PDR, on PRP only"
))

@@

# Export all individual imputation results for transparency
if (exists("all_mfx_results") && length(all_mfx_results) > 0) {
  all_imp_df <- do.call(rbind, lapply(names(all_mfx_results), function(sg_name) {
    sg_results <- all_mfx_results[[sg_name]]
    do.call(rbind, lapply(seq_along(sg_results), function(i) {
      res <- sg_results[[i]]
      if (!is.null(res) && !is.null(res$success) && res$success) {
        data.frame(
          subgroup = sg_name,
          imputation = i,
          ame = res$ame,
          se = res$se,
          n = res$n,
          stringsAsFactors = FALSE
        )
      }
    }))
  }))

  if (!is.null(all_imp_df) && nrow(all_imp_df) > 0) {
    write.csv(all_imp_df,
              file.path(marginal_effects_dir, "all_imputation_results.csv"),
              row.names = FALSE)
    cat("✓ Individual imputation results saved to: all_imputation_results.csv\n")
  }
}

log_message("Results exported")
cat("\n✓ All results exported to:", marginal_effects_dir, "\n")
cat("\nExported files:\n")
cat("  - marginal_effects_summary.csv (formatted table)\n")
cat("  - marginal_effects_numeric.csv (numeric values)\n")
cat("  - all_imputation_results.csv (individual imputations)\n")
cat("  - marginal_effects_summary.txt (text summary)\n")
cat("  - marginal_effects_export.rds (complete R object)\n")
cat("  - forest_plot_*.png (visualization)\n")
```

### 2025-09-08 reanalysis-14-export_results.qmd
reorganize

---
title: "Step 12: Export Results"
subtitle: "Export pooled results and key findings to various formats"
author: "Analysis Team"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
    embed-resources: true
    self-contained: true
---

@@

# Configuration
pooled_cache_dir <- file.path(reanalysis_data_dir, "ps_cache", "pooled_results")
export_dir <- file.path(reanalysis_data_dir, "exported_results")

@@

## Load Pooled Results

```{r load-results}
# Load the pooled results
pooled_results_file <- file.path(pooled_cache_dir, "all_pooled_results.rds")

if (!file.exists(pooled_results_file)) {
  stop(paste0("Pooled results not found at: ", pooled_results_file, "\n",
              "Please run reanalysis-10-pooling_results.qmd first"))
}

pooled_results <- readRDS(pooled_results_file)
log_message(paste0("Loaded pooled results for ", length(pooled_results), " methods"))

# Display structure of first method to show what we're working with
cat("Structure of pooled results (first method):\n")
str(pooled_results[[1]])
```

@@

>>>>

---
title: "Step 14: Export All Results"
subtitle: "Export pooled PS results, marginal effects, and forest plots to various formats"
author: "Analysis Team"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show code"
    embed-resources: true
    self-contained: true
---

@@

# Configuration
pooled_cache_dir <- file.path(reanalysis_data_dir, "ps_cache", "pooled_results")
marginal_effects_dir <- file.path(reanalysis_data_dir, "marginal_effects_cache")
forest_plots_dir <- file.path(reanalysis_data_dir, "forest_plots")
export_dir <- file.path(reanalysis_data_dir, "exported_results")

@@

## Load All Results

```{r load-results}
# Load PS methods pooled results
pooled_results_file <- file.path(pooled_cache_dir, "all_pooled_results.rds")

if (file.exists(pooled_results_file)) {
  pooled_results <- readRDS(pooled_results_file)
  log_message(paste0("Loaded pooled PS results for ", length(pooled_results), " methods"))
} else {
  cat("Warning: PS pooled results not found. Run reanalysis-10-pooling_results.qmd first\n")
  pooled_results <- list()
}

# Load marginal effects results
mfx_results_file <- file.path(marginal_effects_dir, "pooled_mfx_results.rds")

if (file.exists(mfx_results_file)) {
  pooled_mfx <- readRDS(mfx_results_file)
  log_message(paste0("Loaded marginal effects for ", length(pooled_mfx), " subgroups"))
} else {
  cat("Warning: Marginal effects results not found. Run reanalysis-12-marginal_effects.qmd first\n")
  pooled_mfx <- list()
}

# Check for forest plots
forest_plot_files <- list.files(forest_plots_dir, pattern = "\\.png$", full.names = TRUE)
if (length(forest_plot_files) > 0) {
  log_message(paste0("Found ", length(forest_plot_files), " forest plot files"))
} else {
  cat("Warning: No forest plots found. Run reanalysis-13-forest_plots.qmd first\n")
}
```

@@

## Export 5: Marginal Effects Results (CSV)

```{r export-ame-csv}
if (length(pooled_mfx) > 0) {
  # Create formatted AME table
  ame_df <- do.call(rbind, lapply(names(pooled_mfx), function(sg_name) {
    res <- pooled_mfx[[sg_name]]
    if (!is.null(res) && res$success) {
      data.frame(
        subgroup = sg_name,
        subgroup_label = res$name,
        ame = res$ame,
        se = res$se,
        ci_lower = res$ci_lower,
        ci_upper = res$ci_upper,
        z_stat = res$z_stat,
        p_value = res$p_value,
        avg_n = res$avg_n,
        n_imputations = res$n_imputations,
        stringsAsFactors = FALSE
      )
    }
  }))

  if (!is.null(ame_df) && nrow(ame_df) > 0) {
    # Save numeric version
    ame_csv_file <- file.path(export_dir, "marginal_effects_pooled.csv")
    write.csv(ame_df, ame_csv_file, row.names = FALSE)
    log_message(paste0("Exported AME results to: ", ame_csv_file))

    # Create formatted version for display
    ame_formatted <- data.frame(
      Subgroup = ame_df$subgroup_label,
      AME = sprintf("%.4f", ame_df$ame),
      SE = sprintf("%.4f", ame_df$se),
      `95% CI` = sprintf("(%.4f, %.4f)", ame_df$ci_lower, ame_df$ci_upper),
      `P-value` = ifelse(ame_df$p_value < 0.001, "<0.001", sprintf("%.3f", ame_df$p_value)),
      `Avg N` = sprintf("%.0f", ame_df$avg_n),
      stringsAsFactors = FALSE,
      check.names = FALSE
    )

    ame_formatted_file <- file.path(export_dir, "marginal_effects_formatted.csv")
    write.csv(ame_formatted, ame_formatted_file, row.names = FALSE)

    # Display summary
    cat("\n", paste(rep("=", 60), collapse = ""), "\n")
    cat("MARGINAL EFFECTS EXPORT SUMMARY\n")
    cat(paste(rep("=", 60), collapse = ""), "\n\n")
    cat("Number of subgroups:", nrow(ame_df), "\n")
    cat("Overall AME:", sprintf("%.4f", ame_df$ame[ame_df$subgroup == "overall"]), "\n")
    cat("Files exported:\n")
    cat("  - marginal_effects_pooled.csv (numeric)\n")
    cat("  - marginal_effects_formatted.csv (publication-ready)\n\n")
  }
} else {
  cat("No marginal effects results to export\n")
}
```

## Export 6: Combined Results Summary

```{r export-combined}
# Create a comprehensive summary combining PS methods and AME results
if (length(pooled_results) > 0 || length(pooled_mfx) > 0) {
  combined_summary <- list()

  # Add PS methods summary
  if (length(pooled_results) > 0) {
    ps_summary <- data.frame(
      analysis = "PS Methods",
      method = names(pooled_results),
      estimate_type = "OR",
      estimate = sapply(pooled_results, function(x) if(x$success) x$or else NA),
      ci_lower = sapply(pooled_results, function(x) if(x$success) x$or_ci_lower else NA),
      ci_upper = sapply(pooled_results, function(x) if(x$success) x$or_ci_upper else NA),
      p_value = sapply(pooled_results, function(x) if(x$success) x$p_value else NA),
      stringsAsFactors = FALSE
    )
    combined_summary$ps_methods <- ps_summary
  }

  # Add AME summary
  if (length(pooled_mfx) > 0) {
    ame_summary <- data.frame(
      analysis = "Marginal Effects",
      method = names(pooled_mfx),
      estimate_type = "AME",
      estimate = sapply(pooled_mfx, function(x) if(x$success) x$ame else NA),
      ci_lower = sapply(pooled_mfx, function(x) if(x$success) x$ci_lower else NA),
      ci_upper = sapply(pooled_mfx, function(x) if(x$success) x$ci_upper else NA),
      p_value = sapply(pooled_mfx, function(x) if(x$success) x$p_value else NA),
      stringsAsFactors = FALSE
    )
    combined_summary$marginal_effects <- ame_summary
  }

  # Combine all results
  combined_df <- do.call(rbind, combined_summary)
  combined_file <- file.path(export_dir, "all_results_combined.csv")
  write.csv(combined_df, combined_file, row.names = FALSE)

  log_message(paste0("Exported combined results to: ", combined_file))
  cat("\nCombined results exported to: all_results_combined.csv\n")
}
```

## Export 7: Copy Forest Plots

```{r export-forest-plots}
# Copy forest plots to export directory if they exist
if (length(forest_plot_files) > 0) {
  cat("\n", paste(rep("=", 60), collapse = ""), "\n")
  cat("COPYING FOREST PLOTS\n")
  cat(paste(rep("=", 60), collapse = ""), "\n\n")

  for (plot_file in forest_plot_files) {
    dest_file <- file.path(export_dir, basename(plot_file))
    file.copy(plot_file, dest_file, overwrite = TRUE)
    cat("Copied:", basename(plot_file), "\n")
  }

  log_message(paste0("Copied ", length(forest_plot_files), " forest plots to export directory"))
}

# Also copy AME-specific CSV files if they exist
ame_csv_files <- c(
  file.path(marginal_effects_dir, "marginal_effects_summary.csv"),
  file.path(marginal_effects_dir, "marginal_effects_numeric.csv"),
  file.path(marginal_effects_dir, "all_imputation_results.csv")
)

for (csv_file in ame_csv_files) {
  if (file.exists(csv_file)) {
    dest_file <- file.path(export_dir, basename(csv_file))
    file.copy(csv_file, dest_file, overwrite = TRUE)
    cat("Copied:", basename(csv_file), "\n")
  }
}
```
